---
title: "Processing raw curvature images"
author: "Tina Lasisi"
date: "`r Sys.time()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
This documents the entire processing pipeline from raw curvature image to parameter estimation.
```{r}
library(tidyverse)

F = rprojroot::is_rstudio_project$make_fix_file()

knitr::opts_chunk$set(echo = TRUE, include = TRUE, eval = TRUE, warning = FALSE, message = FALSE)
```

## Renaming images

```{r, eval=FALSE}

# imdir <- "/Users/tpl5158/Box/PNG_SA_CURVATURE/"
#Import CSV file with old and new names as dataframe
rename_sh <- read.csv(F("data/PNG_curv_renaming_sheet.csv"))

#Add filetype to names
rename_sh <- rename_sh %>% 
  mutate(old = paste0("P", old, ".RW2"),
         new = paste0(new, ".RW2"))

# Create vectors with complete file path
old.names <- as.vector(paste0("/Users/tpl5158/Box/PNG_SA_CURVATURE/20200817Dump/", rename_sh$old))
dir.create("/Users/tpl5158/Box/01_TPL5158/PNG_hairs/data/PNG_curv_raw/")
new.names <- as.vector(paste0("/Users/tpl5158/Box/01_TPL5158/PNG_hairs/data/PNG_curv_raw/", rename_sh$new))

# check the names
head(old.names)
head(new.names)
# check number of files
length(old.names)
length(new.names)

# Use copy to rename the files without altering originals
file.copy(from = old.names, to = new.names)


```

## Converting images to grayscale

First go to correct directory.
```{bash, eval=FALSE}
cd /Users/tpl5158/Box/01_TPL5158/PNG_hairs
```

Then activate conda environment.
```{bash, eval=FALSE}
conda activate fibermorph_env
```

Update conda.
```{bash, eval=FALSE}
conda update --all
```

Update fibermorph.
```{bash, eval=FALSE}
pip install fibermorph -U
```

Added raw images from previous data acquisition.

Finally, convert raw images to grayscale
```{bash, eval=FALSE}
fibermorph --raw2gray -i data/PNG_curv_raw -o data --jobs 4
```
When I ran this on Dec 16, 2020 (13:01), it processed 67 files in 52s (1.27 files/s).

## Get cross-sectional parameters (without saved images)
```{bash, eval=FALSE}
fibermorph --curvature -i data/PNG_curv_tiff -o data --resolution_mm 132  --jobs 4
```

When I ran this on Dec 16, 2020 (15:19), it processed 67 files in 20m 35s (18.43s/file)

Then check the file 
```{r}

curvature_df <- read.csv("data/Dec16_1519_fibermorph_curvature/curvature_summary_data_Dec16_1540.csv")

head(curvature_df)
```


If everything is as expected, delete unnecessary columns and save.
```{r}
curvature_df_out <- as_tibble(curvature_df) %>% 
  select(-X) %>% 
  mutate(ID = as_factor(sort(as.numeric(str_remove_all(ID, "PNG"))))) %>% 
  write.csv("data/curvature_df.csv", row.names = FALSE)
```

