---
title: "Renaming & converting raw section images"
author: "Tina Lasisi"
date: "`r Sys.time()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r}
library(tidyverse)

F = rprojroot::is_rstudio_project$make_fix_file()

knitr::opts_chunk$set(echo = TRUE, include = TRUE, eval = TRUE, warning = FALSE, message = FALSE)
```

## Renaming images

```{r, eval=FALSE}

imdir <- "/Users/tpl5158/Box/PNG_section_images"
#Import CSV file with old and new names as dataframe
rename_sh <- read.csv("data/PNG_renaming_sheet.csv")

#Add filetype to names
rename_sh <- rename_sh %>% 
  mutate(old = paste0(old, ".RW2"),
         new = paste0(new, ".RW2"))

# Create vectors with complete file path
old.names <- as.vector(paste0("/Users/tpl5158/Box/PNG_section_images/", rename_sh$location, "/", rename_sh$old))
new.names <- as.vector(paste0("/Users/tpl5158/Box/01_TPL5158/PNG_hairs/data/", "PNG_raw/", rename_sh$new))

# check the names
head(old.names)
head(new.names)
# check number of files
length(old.names)
length(new.names)

# Use copy to rename the files without altering originals
file.copy(from = old.names, to = new.names)


```

## Converting images to grayscale

First go to correct directory.
```{bash, eval=FALSE}
cd /Users/tpl5158/Box/01_TPL5158/PNG_hairs
```

Then activate conda environment.
```{bash, eval=FALSE}
conda activate fibermorph_env
```

Update conda.
```{bash, eval=FALSE}
conda update --all
```

Update fibermorph.
```{bash, eval=FALSE}
pip install fibermorph -U
```

Finally, convert raw images to grayscale
```{bash, eval=FALSE}
fibermorph --raw2gray -i data/PNG_raw -o data --jobs 4
```
When I ran this on Dec 11, 2020 (11:55), it processed 335 files in 4m 7s (1.35 files/s).

## Get cross-sectional parameters
```{bash, eval=FALSE}
fibermorph --section -i data/tiff -o data --minsize 20 --maxsize 150 --resolution_mu 4.25 --jobs 4
```

When I ran this on Dec 11, 2020 (12:08), it processed 335 files in 7m 48s (1.40s/file)

Then check the file 
```{r}

section_df <- read.csv("data/Dec11_1208_fibermorph_section/summary_section_data.csv")

head(section_df)
```

If everything is as expected, separate the hairs per ID and calculate summary values and save as spreadsheet
```{r}
section_df_out <- as_tibble(section_df) %>% 
  separate(col = ID, into = c("ID", "hair")) %>% 
  group_by(ID) %>% 
  summarise(across(where(is.numeric), list(median = median, mean = mean, sd = sd), .names = "{.col}_{.fn}")) %>% 
  write.csv("data/section_df.csv")
```

